### 2010-08-10 doc/manuals/chelonia/arc-storage-manual.tex
Switching documents to bibliography style which is supposed to be present in latex distributions. Fixes in some documents and build procedures.
ca_dir instead of cacert

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {Administrator's manual of the ARC storage system},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\bibliographystyle{IEEEtran}                       %a nice bibliography style
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

cacert=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia1.pem
host_key=/etc/grid-security/hostkey-chelonia1.pem
client_cert=/etc/grid-security/hostcert-chelonia1.pem
client_key=/etc/grid-security/hostkey-chelonia1.pem

@@

cacert=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia2.pem
host_key=/etc/grid-security/hostkey-chelonia2.pem
client_cert=/etc/grid-security/hostcert-chelonia2.pem
client_key=/etc/grid-security/hostkey-chelonia2.pem

@@

cacert=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia3.pem
host_key=/etc/grid-security/hostkey-chelonia3.pem
client_cert=/etc/grid-security/hostcert-chelonia3.pem
client_key=/etc/grid-security/hostkey-chelonia3.pem

>>>>

\documentclass{article}
%\documentclass{book}
\usepackage{graphicx}                              %for PNG images (pdflatex)
\usepackage[linkbordercolor={1.0 1.0 0.0}]{hyperref} %for \url tag
\usepackage{color}                                 %for defining custom colors
\usepackage{framed}                                %for shaded and framed paragraphs
\usepackage{textcomp}                              %for various symbols, e.g. Registered Mark
\usepackage{geometry}                              %for defining page size
\usepackage{longtable}                             %for breaking tables
%
\geometry{verbose,a4paper,tmargin=2.5cm,bmargin=2.5cm,lmargin=2.5cm,rmargin=2cm}
\hypersetup{
  pdfauthor = {Zsombor Nagy},
  pdftitle = {Administrator's manual of the ARC storage system},
  pdfsubject = {Paper subject},
  pdfkeywords = {Paper,keyword,comma-separated},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}
%
\usepackage[numbers]{natbib}
\bibliographystyle{plainnat}
%
\def\efill{\hfill\nopagebreak}%
\hyphenation{Nordu-Grid}
\setlength{\parindent}{0cm}
\setlength{\FrameRule}{1pt}
\setlength{\FrameSep}{8pt}
\addtolength{\parskip}{5pt}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\arraystretch}{1.3}
\newcommand{\dothis}{\colorbox{shadecolor}}
\newcommand{\ngdl}{\url{http://ftp.nordugrid.org/download}~}
\definecolor{shadecolor}{rgb}{1,1,0.6}
\definecolor{salmon}{rgb}{1,0.9,1}
\definecolor{bordeaux}{rgb}{0.75,0.,0.}
\definecolor{cyan}{rgb}{0,1,1}
%
%----- DON'T CHANGE HEADER MATTER
\hyphenation{preserve-Original}
\begin{document}
\def\today{\number\day/\number\month/\number\year}

@@

ca_dir=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia1.pem
host_key=/etc/grid-security/hostkey-chelonia1.pem
client_cert=/etc/grid-security/hostcert-chelonia1.pem
client_key=/etc/grid-security/hostkey-chelonia1.pem

@@

ca_dir=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia2.pem
host_key=/etc/grid-security/hostkey-chelonia2.pem
client_cert=/etc/grid-security/hostcert-chelonia2.pem
client_key=/etc/grid-security/hostkey-chelonia2.pem

@@

ca_dir=/etc/grid-security/certificates
host_cert=/etc/grid-security/hostcert-chelonia3.pem
host_key=/etc/grid-security/hostkey-chelonia3.pem
client_cert=/etc/grid-security/hostcert-chelonia3.pem
client_key=/etc/grid-security/hostkey-chelonia3.pem
